SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-18 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf paper: Modifications and replies to reviewers by Simon: - 1 in the introduction re lack in previous work on BIP architectures - 1 in the conclusion re scalability

\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
%\newcommand{\TODO}[1]{}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\newcommand{\OTvar}{\texttt}
\newcommand{\OTland}{\;\land\ }
\definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}

@@

BIP
(Behaviour-Interaction-Priority)~\cite{bip} is a framework for 
component-based design of concurrent software and systems.  In
particular, the BIP tool-set comprises compilers for generating C/C++
code, executable by linking with one of the dedicated engines, which
implement the BIP operational semantics~\cite{BarBliu15-offer-scico}.  This
approach ensures that any property, shown to hold on a given BIP
model, will also hold by construction on the generated code.
BIP architectures~\cite{AttieBBJS16-architectures-faoc} formalise
design patterns, which enforce global properties 
characterising the coordination among the components of the
system. They provide a compositional approach, ensuring
correctness by construction during the design of BIP models.
In~\cite{AttieBBJS16-architectures-faoc}, it was shown that
application of architectures is compositional \wrt safety properties,
\ie when several architectures are applied, each enforcing a safety
property, the resulting system satisfies their conjunction.

But the interaction feature in architectures does not handle
data-sensitive interaction constraints. Using an encoding of
architectures, extended with data-dependent interactions, into open
pNets was an interesting alternative to a direct extension to the
architecture semantics.

@@

We validate the approach on two larger examples, 
based on a BIP architecture taken from an earlier nanosatellite case
study~\cite{CubETH-case-study}. We also show how such architectures
can be composed, and how our approach scales.
This example shows that
open-automata-based semantics can be instrumental in verifying the
properties enforced by the architectures through an encoding into open
pNets.
We also compare the practical performances of the two algorithms and
show the benefit gained using the smart approach.

>>>>

\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
%\newcommand{\TODO}[1]{}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\newcommand{\OTvar}{\texttt}
\newcommand{\OTland}{\;\land\ }
\definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\definecolor{darkgreen}{rgb}{0.2, 0.55, 0.2}
\newcommand{\Simon}[1]{\textcolor{darkgreen}{#1}}

@@

BIP
(Behaviour-Interaction-Priority)~\cite{bip} is a framework for 
component-based design of concurrent software and systems.  In
particular, the BIP tool-set comprises compilers for generating C/C++
code, executable by linking with one of the dedicated engines, which
implement the BIP operational semantics~\cite{BarBliu15-offer-scico}.  This
approach ensures that any property, shown to hold on a given BIP
model, will also hold by construction on the generated code.
BIP architectures~\cite{AttieBBJS16-architectures-faoc} formalise
design patterns, which enforce global properties 
characterising the coordination among the components of the
system. They provide a compositional approach, ensuring
correctness by construction during the design of BIP models.
In~\cite{AttieBBJS16-architectures-faoc}, it was shown that
application of architectures is compositional \wrt safety properties,
\ie when several architectures are applied, each enforcing a safety
property, the resulting system satisfies their conjunction.
%
\Simon{However, \cite{AttieBBJS16-architectures-faoc} did not provide
  any mechanism for verifying the correctness of individual
  architectures.  The encoding presented in this paper provides such a
  mechanism.}

\st{But the interaction feature in architectures does not handle
data-sensitive interaction constraints. Using an encoding of
architectures, extended with data-dependent interactions, into open
pNets was an interesting alternative to a direct extension to the
architecture semantics.}

@@

We validate the approach on \Simon{a larger example}\st{two larger examples}, 
based on a BIP architecture taken from an earlier nanosatellite case
study~\cite{CubETH-case-study}.  \Simon{This example shows that
open-automata-based semantics can be instrumental in verifying the
properties enforced by the architectures through an encoding into open
pNets.
In order to evaluate the potential
%
of our approach to scale to larger systems, we also apply the proposed
techniques to a BIP architecture obtained by combining two instances
of the Failure Monitor architecture.  Our results show that, even
though, the performance of the smart algorithm degrades more than
linearly, execution times remain reasonably small.  It should be noted
that the aim of our approach, particularly in the case of BIP
architectures, is to allow symbolic verification of design patterns to
show that they do impose corresponding properties. Safety of the system is obtained compositionally, whereas liveness is verified by checking \emph{pair-wise} non-interference.
%
}\st{We also show how such architectures
can be composed, and how our approach scales.
This example shows that
open-automata-based semantics can be instrumental in verifying the
properties enforced by the architectures through an encoding into open
pNets.
We also compare the practical performances of the two algorithms and
show the benefit gained using the smart approach.}
